Covariate analysis of MAYO reprocessed counts (with TMM normalisation)

### 2017-03-08 code/Rmd/MSSM_RNASeq_Reprocessed_TMM_BinnedCDR.Rmd
Minor bug fix

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                                COVARIATES,
                                                'all adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

@@

tmp = DE1 %>% 
  dplyr::filter(adj.P.Val <= 0.05) %>%
  group_by(Region, Comparison) %>%
  summarise(count = length(unique(genes))) %>%
  tidyr::spread(Region, Comparison)
kable(tmp)
```

>>>>

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                                COVARIATES[,residCovars,drop = F],
                                                'all adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

@@

tmp = DE1 %>% 
  dplyr::filter(adj.P.Val <= 0.05) %>%
  group_by(Region, Comparison) %>%
  summarise(count = length(unique(gene.id))) %>%
  tidyr::spread(Region, count)
kable(tmp)
```

### 2017-03-08 code/Rmd/Mayo_RNASeq_Reprocessed_TMM.Rmd
Minor bug fix

@@

### Data preprocessing
```{r preprocess.data,cache=FALSE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA$BrainRegion.Diagnosis = paste(METADATA$BrainRegion, METADATA$Diagnosis, sep = '.')
METADATA$RIN2 = METADATA$RIN^2
METADATA <- METADATA %>%
  filter(!is.na(Source)) %>%
  dplyr::filter(!(ID %in% c("11311_CER", "1923_CER", "1923_TCX", 
                            "11396_TCX", "11294_TCX", "11408_TCX")))
```
Following samples were considered outliers and removed based on PCA and/or eucledian distance: 11311\_CER, 1923\_CER, 1923\_TCX, 11396\_TCX, 11294\_TCX, 11408\_TCX
```{r preprocess.data1}
# Match covariates to expression data
indToRetain = intersect(METADATA$ID, colnames(COUNT))
indRemoved = setdiff(colnames(COUNT), METADATA$ID)

@@

plotdata[grep('CER', plotdata$ID),'Region'] = 'CER'
plotdata[grep('TCX', plotdata$ID),'Region'] = 'TCX'
plotdata$Region = factor(plotdata$Region)
plotdata$Source = factor(plotdata$Source)

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape = Source, color = Region))
p <- p + theme_bw() + theme(legend.position = "left") +scale_shape_manual(values = 1:2)
p <- p + facet_grid(Region~.)
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
p
```
```{r decompse.normalise.data2, fig.height=9, fig.width=25, results='asis'}
# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(VOOM.GENE_EXPRESSION$E)), method = "average")
tree = WGCNA::cutreeStatic(sampleTrees, cutHeight = 135, minSize=10)

>>>>

library(ComplexHeatmap)
library(circlize)

@@

### Data preprocessing
```{r preprocess.data,cache=FALSE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA$BrainRegion.Diagnosis = paste(METADATA$BrainRegion, METADATA$Diagnosis, sep = '.')
METADATA$RIN2 = METADATA$RIN^2
METADATA <- METADATA %>%
  filter(!is.na(Source))
# %>%
#   dplyr::filter(!(ID %in% c("11311_CER", "1923_CER", "1923_TCX", 
#                             "11396_TCX", "11294_TCX", "11408_TCX")))
```
Following samples were considered outliers and removed based on PCA and/or eucledian distance: 11311\_CER, 1923\_CER, 1923\_TCX, 11396\_TCX, 11294\_TCX, 11408\_TCX
```{r preprocess.data1}
# Match covariates to expression data
indToRetain = intersect(METADATA$ID, colnames(COUNT))
indRemoved = setdiff(colnames(COUNT), METADATA$ID)

@@

plotdata[grep('CER', plotdata$ID),'Region'] = 'CER'
plotdata[grep('TCX', plotdata$ID),'Region'] = 'TCX'
plotdata$Region = factor(plotdata$Region)
plotdata$Source = factor(plotdata$Source)
plotdata$ID[!(plotdata$ID %in% c("11311_CER", "1923_CER", "1923_TCX", "11396_TCX", "11294_TCX", "11408_TCX"))] = ''

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape = Source, color = Region))
p <- p + theme_bw() + theme(legend.position = "right") +scale_shape_manual(values = 1:2)
p <- p + facet_grid(Region~.)
p <- p + geom_text(aes(label= ID), size=4, hjust=1, vjust=-1)
p
```
```{r decompse.normalise.data2, fig.height=9, fig.width=25, results='asis'}
# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(VOOM.GENE_EXPRESSION$E)), method = "average")
tree = WGCNA::cutreeStatic(sampleTrees, cutHeight = 135, minSize=10)
